---
title: "German Climate Data"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
---
	
	
```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
		   cache=FALSE,
		   prompt=FALSE,
		   tidy=FALSE,
		   comment=NA,
		   message=FALSE,
		   warning=FALSE)
opts_knit$set(width=75)
```

## Load Libraries
```{r load_libs, echo=FALSE, cache=FALSE}
library(plyr)
library(dplyr)
library(tidyr)
```

## Pre-processing
```
ls -1 | wc -l							# count files in a dir
awk -F\" '{print $2}' source.txt > names.txt		# trim html code for filenames
awk '{print "ftp://ftp-cdc.dwd.de/pub/CDC/observations_germany/climate/monthly/more_precip/historical/" $0;}' names.txt > filelist.txt							# create filenames using prefix.txt
```

## File Retrieval
```
wget -i filelist.txt		# download all files
for i in *.zip; do unzip "$i"; done		# extract all zips
cp [S]* outputfolder		# copying files of same name
```


# Read in Data
``` {r dat-read, echo=TRUE}
files <- dir(pattern = '*.txt', full.names = TRUE)
tables.of.data <- lapply(files, read.table,sep=";",header=TRUE,fill=TRUE)
```

# Subset and Trim
```{r dat-subset, echo=TRUE}
# correcting for false factors in data

fix.factors <-function(df) {
  df[complete.cases(df),]
}
tables.of.data.trimmed<-lapply(tables.of.data,fix.factors)
# subset columns of interest
tables.subset<-lapply(tables.of.data.trimmed,"[",1:6)
# remove un-needed datafiles
rm(tables.of.data.trimmed); rm(tables.of.data)

```







tables.of.data.trimmed<-lapply(tables.of.data,fix.factors)

# subset columns of interest
tables.subset<-lapply(tables.of.data.trimmed,"[",1:6)

# remove un-needed datafiles
rm(tables.of.data.trimmed); rm(tables.of.data)


# test plot
plot(tables.subset[[1]]$NIEDERSCHLAGSHOEHE,type="l")

# OR convert to BIG df
data.df<-dplyr::bind_rows(tables.subset)

# deal with FALSE factors
data.df.FF<-data.df[complete.cases(data.df),] # remove NA's (false factors and missing data)

# Various Cleaning

data.df.FF$date.start <-as.character(data.df.FF$MESS_DATUM_BEGINN) %>% as.Date(., format='%Y%m%d')
data.df.FF$date.end <-as.character(data.df.FF$MESS_DATUM_ENDE) %>% as.Date(., format='%Y%m%d')

data.df.FF$station.id <- as.factor(data.df.FF$STATIONS_ID)
data.df.FF$precip <- data.df.FF$NIEDERSCHLAGSHOEHE

dt <- data.df.FF %>% select(date.start:precip)
dt$precip[dt$precip==-999] <- NA

dt.ts <- as.ts(dt)

# remove un-needed datafiles
rm(data.df); rm(data.df.FF);


#########################
# Quick Look at Data


#--->>> merging id data
new<-read.table("stat.csv",header=TRUE, sep =",")
dat = as.data.table(dt.arranged)
dat2 = as.data.table(new)
dat2$station.id <-dat2$stat_id

newdt<-merge(dat, dat2, by="station.id")

write.dir <- "downloads/product/figs/"


ii <- unique(newdt$locale)
i<-unique(newdt$station.id)

n<-1
                                               
for (n in n:150){                                               
png(filename = paste(write.dir,"Fig-",ii[n],".png",sep=""))
print(xyplot(precip ~ date.start |locale , data = newdt, layout=c(1,1,ii[n]),as.table=FALSE,
strip=TRUE, pch = 16, type=c("l"),col.line="blue",horizontal=FALSE, aspect="free",
ylab = "Precipation (mm)", xlab = "Years",
panel = function (x,y, ...){
panel.xyplot(x,y, ...)
}))
dev.off()
}




########################
library(zoo)

# Example of using a custom axis
# Months are labelled with smaller ticks for weeks and even smaller
# ticks for days.
Days <- seq(from = as.Date("2006-1-1"), to = as.Date("2006-8-8"), by = "day")
z <- zoo(seq(length(Days))^2, Days)
Months <- Days[format(Days, "%d") == "01"]
Weeks <- Days[format(Days, "%w") == "0"]
xyplot(z, scales = list(x = list(at = Months)))
trellis.focus("panel", 1, 1, clip.off = TRUE)
panel.axis("bottom", check.overlap = TRUE, outside = TRUE, labels = FALSE, 
  tck = .7, at = as.numeric(Weeks))
panel.axis("bottom", check.overlap = TRUE, outside = TRUE, labels = FALSE, 
  tck = .4, at = as.numeric(Days))
trellis.unfocus()


z <-as.ts(dt)
zz<-na.omit(z)


tablesmin[[1]]$stat<-as.character(tablesmin[[1]]$STATIONS_ID)
out$stat <-as.factor(out$STATIONS_ID)


new<-read.table("stat.csv",header=TRUE, sep =",")
dataTable <- read.table("names.txt",header=T)

read.csv("stat.csv")




